---
title: "News"
format:
  html:
    page-layout: article
    toc: false
execute:
  echo: false
  warning: false
  message: false
---

## The Wire

```{r editions-margin}
#| results: asis
source("scripts/shared.R")

# Quick links to the class newspaper's editions, kept in the right margin.
newspaper <- load_intake_editions()

if (nrow(newspaper) > 0 && all(c("Edition", "Link") %in% names(newspaper))) {
  eds <- newspaper |> filter(!is.na(Link) & Link != "")
  if (nrow(eds) > 0) {
    eds <- eds[rev(seq_len(nrow(eds))), ]  # newest first
    items <- sprintf(
      '<li><a href="%s" target="_blank" rel="noopener">%s</a>%s</li>',
      eds$Link,
      ifelse(grepl("^[0-9]+$", eds$Edition), paste("Edition", eds$Edition), eds$Edition),
      ifelse(is.na(eds$Date) | eds$Date == "", "", paste0(" · ", eds$Date))
    )
    cat('::: {.column-margin}\n',
        '<div class="margin-editions"><span class="margin-label">Class Newspaper</span><ul>',
        paste(items, collapse = ""),
        '</ul></div>\n',
        ':::\n', sep = "")
  }
}
```

Live dispatches from the press corps — newest first.

```{r press-links}
#| results: asis
pw <- form_url("Posts"); pe <- form_url("Editions")
links <- c(
  if (!is.na(pw)) sprintf('<a href="%s">Post to the Wire</a>', pw),
  if (!is.na(pe)) sprintf('<a href="%s">Publish an edition</a>', pe)
)
if (length(links) > 0)
  cat('<p class="table-note">', paste(links, collapse = " · "), '</p>', sep = "")
```

<div class="wire-feed"></div>
<script src="js/feed.js"></script>

## The Papers

```{r outlets}
#| results: asis
# The outlet directory as tiles: each paper's FULL name as its
# nameplate, in journalist purple (the role's canonical color), type
# sized to the name's length. The face links to the outlet's article
# page when a Link is set; a "Profile" chip appears at the tile's foot
# once the outlet's uploaded role profile has synced in.
sync_intake_profiles()
news <- tryCatch(read.csv(JOURNALIST_CSV), error = function(e) data.frame())

if (nrow(news) > 0) {
  tiles <- vapply(seq_len(nrow(news)), function(i) {
    outlet <- news$Newspaper[i]
    size <- if (nchar(outlet) <= 12) "1.35rem"
            else if (nchar(outlet) <= 20) "1.12rem" else "0.98rem"
    inner <- sprintf('<span class="tile-title" style="font-size:%s">%s</span>',
                     size, outlet)

    link <- news$Link[i]
    face <- if (!is.na(link) && link != "") {
      sprintf('<a class="tile-face" href="%s" target="_blank" rel="noopener">%s</a>', link, inner)
    } else {
      sprintf('<span class="tile-face">%s</span>', inner)
    }

    profile_pdf <- sprintf("%s/%s_profile.pdf", JOUR_PROFILE_DIR, outlet_slug(outlet))
    chip <- if (file.exists(profile_pdf)) {
      sprintf('<a class="tile-chip" href="%s" target="_blank" rel="noopener">Profile</a>', profile_pdf)
    } else ""

    sprintf('<div class="tile paper">%s%s</div>', face, chip)
  }, character(1))

  cat('<div class="tile-grid">', paste(tiles, collapse = "\n"), '</div>')
} else {
  cat("Newspaper list not available yet.\n")
}
```

<p class="table-note">A note for students: these are real outlets, role-played
for the simulation. Anything you create for the simulation outside this
site — social-media accounts, posts, mock front pages, anything public —
must be clearly marked as fictional UC Merced simulation work, so it can
never be mistaken for the real newspaper.</p>
