---
title: "News"
format:
  html:
    page-layout: full
    toc: false
execute:
  echo: false
  warning: false
  message: false
---

::: {.grid}

::: {.g-col-12 .g-col-lg-7}

## The Wire

Live dispatches from the press corps — newest first.

```{r press-links}
#| results: asis
source("scripts/shared.R")
pw <- form_url("Posts"); pe <- form_url("Editions")
links <- c(
  if (!is.na(pw)) sprintf('<a href="%s">Post to the Wire</a>', pw),
  if (!is.na(pe)) sprintf('<a href="%s">Publish an edition</a>', pe)
)
if (length(links) > 0)
  cat('<p class="table-note">', paste(links, collapse = " · "), '</p>', sep = "")
```

<div class="wire-feed"></div>
<script src="js/feed.js"></script>

:::

::: {.g-col-12 .g-col-lg-5}

## The Papers

```{r editions-links}
#| results: asis
# Quick links to the class newspaper's editions, atop the outlet column.
newspaper <- load_intake_editions()

if (nrow(newspaper) > 0 && all(c("Edition", "Link") %in% names(newspaper))) {
  eds <- newspaper |> filter(!is.na(Link) & Link != "")
  if (nrow(eds) > 0) {
    eds <- eds[rev(seq_len(nrow(eds))), ]  # newest first
    items <- sprintf(
      '<li><a href="%s" target="_blank" rel="noopener">%s</a>%s</li>',
      eds$Link,
      ifelse(grepl("^[0-9]+$", eds$Edition), paste("Edition", eds$Edition), eds$Edition),
      ifelse(is.na(eds$Date) | eds$Date == "", "", paste0(" · ", eds$Date))
    )
    cat('<div class="margin-editions"><span class="margin-label">Class Newspaper</span><ul>',
        paste(items, collapse = ""),
        '</ul></div>', sep = "")
  }
}
```

```{r outlets}
#| results: asis
# The outlet directory as tiles: each paper's FULL name as its
# nameplate, in journalist purple (the role's canonical color), type
# sized to the name's length. Every tile links to the outlet's own page
# (wire history + role profile), which always exists.
news <- tryCatch(read.csv(JOURNALIST_CSV), error = function(e) data.frame())

if (nrow(news) > 0) {
  tiles <- vapply(seq_len(nrow(news)), function(i) {
    outlet <- news$Newspaper[i]
    size <- if (nchar(outlet) <= 12) "1.05rem"
            else if (nchar(outlet) <= 20) "0.9rem" else "0.78rem"
    inner <- sprintf('<span class="tile-title" style="font-size:%s">%s</span>',
                     size, outlet)
    sprintf('<a class="tile paper" href="%s/%s.html">%s</a>',
            JOURNALIST_PAGES_DIR, outlet_slug(outlet), inner)
  }, character(1))

  cat('<div class="tile-grid papers">', paste(tiles, collapse = "\n"), '</div>')
} else {
  cat("Newspaper list not available yet.\n")
}
```

<p class="table-note">A note for students: these are real outlets, role-played
for the simulation. Anything you create for the simulation outside this
site — social-media accounts, posts, mock front pages, anything public —
must be clearly marked as fictional UC Merced simulation work, so it can
never be mistaken for the real newspaper.</p>

:::

:::
